%!TEX root = proj_report_outline.tex
\chapter{Requirements}

\section{Methodology}

The software methodology adopted in this project has been an agile, iterative approach. Each iteration is approximately one week in length and consists of the following actions: requirements analysis, requirements validation, design, development, testing, and documentation. Thus far in the project this approach has worked well. During the early stages of the project identifying all of the requirements would have been infeasible. A Waterfall-like approach would have required contiguous, extended periods of time with the stakeholders from Callaghan Innovation who have a limited amount of time for this project per week. Furthermore, as this project is a prototype with many stakeholders the iterative approach has been essential in being able to adapt to changes throughout the project life cycle. Each iteration's final acceptance testing action with the client has proven essential in guiding the project's shape and discovering requirements for each following iteration.

\section{Previous Work}

To contextualise the requirements identified this section first introduces Callaghan Innovation's previous work on PitchHub. Callaghan Innovation began work on the idea of PitchHub in 2013. Since this time Callaghan Innovation has discerned what functionality a collaborative innovation platform like PitchHub needs to fulfill it's aim of driving innovation by connecting the roles identified in Section \ref{commonRolesInInnovation}.

\subsection{PitchCards Conceptualisation}
As discussed in Chapter \ref{background} the innovation community has very specific purpose and therefore requires special kind of user participation/interaction 