%!TEX root = proj_report_outline.tex
\chapter{Evaluation}

\section{Functionality Evaluation}
Requirement F1 recognises that the primary goal of PitchHub is to facilitate collaboration within the innovation community. Evaluating this requirement has been performed throughout the development of PitchHub. To make the achievement of this requirement measurable the User Stories used in the design of the system have been implemented as the BDD features. The criteria for completing a user story is that it's correspondent BDD feature(s) are satisfied.
\par
To verify that the tests are representative of the actual behaviour a user experiences Selenium has been used for web browser automation. How this works is that the features are interpreted using definitions, these definitions automate the browser interaction, and throughout the features asserts can be places to ensure that the intended behaviour is given. The PitchHub Functional Test Harness process is visualised in Fig

\subsection{Test Harness}

talk about selenium and user stories

\subsection{Test Data}

frequency analysis of data cleaned and given by CI's user trial

seeded given frequency analysis results

\subsection{Results}

\subsection{Performance Evaluation}

wiki: SecretSharing

The disadvantage of unconditionally secure secret sharing schemes is that the storage and transmission of the shares requires an amount of storage and bandwidth resources equivalent to the size of the secret times the number of shares. If the size of the secret were significant, say 1 GB, and the number of shares were 10, then 10 GB of data must be stored by the shareholders

talk about NN threshold

\section{Security Testing Method}

\subsection{Security Testing Scope}

Our threat model consists of resisting at least one shoulder surfing attack from an observer co-located at any position around the tabletop. Camera-based attacks are feasible with most knowledge-based authentication systems; but to defeat camera attacks was not our design goal. The pervasive na- ture of mobile devices instrumented with cameras is of particular concern, but as with other manifestations of this same problem (e.g. at the ATM) we rely upon social conventions to deter active attempts to video record logins.

\subsection{Threat Taxonomy}
