%!TEX root = proj_report_outline.tex
\chapter{Conclusions and Future Work}
This chapter reviews the project's contributions in light of the design requirements, discusses potential future work and finally, surmises the project.

\section{Review}

The project's principal contributions are as follows:

\paragraph{C1: Innovation Role Taxonomy.} For classifying communication layers/platforms facilitating collaboration between the archetypal roles in the innovation community. The relationship semantics between roles in the taxonomy is denoted as either explicitly supported or implicitly supported. Layers/platforms that facilitate innovation collaboration ideally have explicit support for all roles.

\paragraph{C2: UI design.} Built upon the conceptual work done by Callaghan Innovation the final UI implementation was designed to encourage collaboration and be visually appealing. Content templates and wire frames were the key artefacts produced to guide the final implementation.

\paragraph{C3: Architecture.} The architecture designed and implemented is principal in realising the distributed and performance requirements identified. The architecture has also been designed to support ease of extension for future works by embracing a tiered architectural style.

\paragraph{C4: User stories describing collaboration in the innovation community.} 

Existing user stories of collaboration in the innovation community do not exist. As such new user stories were specified with an emphasis on networking/collaborating around ideas. These stories specify the following: engagement of all roles within the innovation community, the ability to scope content's disclosure, and audit who has seen ideas that you have initiated.

\paragraph{C5.1: A PitchHub prototype.} 

Built on the popular Ruby on Rails framework, the prototype was developed to support the user stories specified. Having followed good coding practices this artefact is open to future extensions.

\paragraph{C5.2: A PitchHub prototype deployed to Callaghan Innovation.} 

For internal use within Callaghan Innovation a prototype was deployed following a production configuration: Passenger application server, caching, SSL, and various security measures suggested by OWASP (e.g. ssh hardening, protection against IP spoofing). Visit \url{http://pitchhub.net}.


\paragraph{C5.3: A PitchHub prototype with Shamir's Secret Sharing scheme integrated.} 

Use of the Shamir's Secret Sharing scheme, most commonly used in key services, was integrated into the PitchHub prototype. Sensitive information such as Pitch Points, suggestions, and comments is encrypted using this service providing unconditional security.

\paragraph{C5.4: A PitchHub prototype with Diverse Secret Keepers.} 

In strengthening the security provided by the Secret Sharing scheme, diverse secret keepers were introduced. PitchHub supports the following databases: MongoDB, Postgres, MySQL and SQLite. To maintain \textit{plug-and-play} functionality afforded by MongoBD the configuration of SQL secret keepers has been automated.

\paragraph{C6: Virtualised development environment.}

To make installation and setup of PitchHub as easy as possible the development environment has been virtualised using Vagrant and Chef. This was primarily for the benefit of non-technical stakeholders, but will be equally useful for future maintainers.

\paragraph{C7: Automated deployment process.}
 
To make host configuration and code deployment as easy as possible the deployment process was automated using Capistrano. Deployments can be triggered effortlessly and use GitHub to ensure production reflects the Master branch. Beyond this deployments can be rolled-back easily, this will be useful in the future should any deployments prove to be defective.
\\
\newline
These contributions are instrumental in fulfilling the design requirements identified. The contributions are now considered in light of these requirements.
\\
\newline
C2, C4, and C5.{\em X} all play roles in the fulfilment of requirements D1, D2.1, and D2.2. The user stories created in D1 capture the behaviours required by D1, D2.1, and D2.2. These user stories were used to drive the design process of the UI (C4) that C5.{\em X} ultimately uses to facilitate these behaviours. The strict adherence to the user stories throughout the design and execution of the project has culminated in artefacts that are faithful in their support of the behaviours required. This fulfilment has been verified by Test \rom{1} and thus requirements D1, D2.1, and D2.2 are concluded as fulfilled.

C5.3 and C5.4 contribute to the fulfilment of requirement D2.3. Integrating the Secret Sharing scheme into the prototype and encrypting commercially sensitive data and IP at the Pitch Point level ensures unconditional security in relation to database breaches (of up to \textit{k}). As described in Section \ref{S:evaluationScope} verification of this component was out of scope of this project. Despite this it is believed that requirement D2.3 has been fulfilled to the extent possible within the scope of this project.

C3, C6 and C7 each play roles in satisfying requirement D3. The architecture (C3) aids extensibility through the tiered architecture style adopted. The virtualised development environment (C6) is key in providing portability, enabling \textit{plug-and-play} functionality for all artefact prototype variations (C5.{\em X}). C7 aids in the extensibility of the deployment process, as new tasks and environment targets can be easily added.

C5.{\em X} have been verified as meeting requirement D4 through Tests \rom{3}-\rom{6} against Nielsen's response time thresholds. Specifically, Tests \rom{3}-Tests \rom{5} verify that requests can be fulfilled within the response-time thresholds given the different Secret Sharing configurations and 



\paragraph{D5: The prototype must support a distributed architecture.}




TODO review in light of design requirements

\section{Future Work}

This section discusses potential extensions to the PitchHub prototype.

\subsection{Recommendation Engine}

A potentially useful feature would be if Pitch Cards could be recommended to users based on their ontological profile. This would encourage collaboration through showing users ideas they are more likely to have an interest in. Offline learning is certainly viable, but an interesting challenge would be integrating the recommender to work with the Secret Sharing service in an online learning approach.

\subsection{Usability Extension/Evaluation}

TODO

\subsection{RealMe Integration}

TODO
